---
title: "02-qmd-figures-chunks"
author: "Your Name"
date: today
format: 
  html:
    keep-md: true
    fig-height: 10
    fig-align: center
    fig-asp: 1.5
    fig-format: png
    fig-dpi: 300
---

# Tasks from "Figures tables captions"

- Create a summary of your gapminder data, put it into a table.
- Add a caption to this table.
- Set the number of decimals to 2.
- Create a plot
- Add a caption

```{r}
library(tidyverse)
library(skimr)
```


```{r}
gap <- read_csv(here::here("data", "gapminder.csv"))
gap
```

## Create a summary of gapminder data into a table

- Add a caption
- Set number of decimals to 2

## Adding a figure of gapminder

- Create a plot
- Add a caption


```{r}
```


# Tasks from "Figures tables captions"

- Change the fig-width, fig-height, and fig-format of the figure in the plot above
  - (hint: use tab-complete on the `#|`)
- Add an option to keep the markdown source code 
- Print the code for one of the figures, but not the other (hint: use `echo = `)


# Tasks from "Figures tables captions"

- Download the [gapminder logo](https://www.gapminder.org/wp-content/themes/gapminder2/images/gapminder-logo.svg)
- Put it into a new directory called "figs" (at the top level)
- Insert the image into your "02-qmd-figures-chunks.qmd" Quarto document around where you introduce gapminder.
- Try using both markdown `![]()` syntax, and `knitr::include_graphics()`.
- Hint: Remember to refer to the image in the right spot using here!

# Tasks from "Changing figures"

1. Create three figures, with the respective dimensions (`fig-height` and `fig-width`)
    * 2x2
    * 10x10
    * 4x7
2. Now add to those figures, the following:
    * `fig-align = "center"`
3. Now change the output type to be "svg"

# Tasks from "Changing Figures"

1. Set the global options in the "02-qmd-figures-chunks.qmd" document to set:
  * `fig-height`
  * `fig-width`
  * `fig-format`


# Tasks from "Changing Figures"

- Save your images to a specific directory of your choice

# Tasks from "Math"

- Add some math to this document
