---
title: "05-qmd-bib-polish"
date: today
format: 
  html:
    fig-height: 3
    fig-width: 4
    fig-format: png
execute: 
  echo: false
csl: jcgs.csl
bibliography: references.bib
---

# Tasks

Add a final heading in your file called #bibliography
Render the document

1.  Generate a references.bib file to place your citations
2.  Using the `citation()` function, generate citations for the packages we have used, "dplyr", "ggplot2", "gapminder", and for the R software, place these in your `references.bib` file
3.  Reference these in your document
4.  Add a final heading in your file called `#bibliography`
5.  Cite the packages you use when you use them
    1.  hint: https://quarto.org/docs/authoring/footnotes-and-citations.html
    2.  hint: look at the names in packages.bib
6.  Tidy up the structure, provide some more words around the introduction and results
7.  Render the document

# Tasks

1. select your bibliography style to be one from your favourite journal at the CSL github repo here: https://github.com/citation-style-language/styles (> 2,600 citations and counting)
2. place this in your rstudio project
3. refer to it in the YAML
4. Render your document and observe your greatness

# Tasks

1 Generate a bibliography and an appendix that follows it

# Introduction

This is a simple analysis of the New York Air Quality Measurements using the R statistical programming language (CITATION PLEASE!). As stated in the helpfile `?airquality`, this dataset contains:

> Daily air quality measurements in New York, May to September 1973.

And the dataset is sourced from:

> ... the New York State Department of Conservation (ozone data) and the National Weather Service (meteorological data).

It contains the following variables

-   Ozone: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island.
-   Solar.R: Solar radiation in Langleys in the frequency band 4000–7700 Angstroms from 0800 to 1200 hours at Central Park.
-   Wind: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport.
-   Temp: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.
-   Month: Month (1--12)
-   Day: Day of month (1--31)

We are going to explore the relationship between solar radiation and other selected variables, solar radiation, wind, and temperature.

[@donoho2017]

# Method

```{r}
#| label: lm-fit

lm_fit <- lm(Ozone ~ Solar.R + Temp + Wind, 
             data = airquality)

```

$$
Ozone \sim \beta_0 + \beta_1Solar.R + \beta_2 Wind + \beta_3Temp + \epsilon
$$

# Results

We can see that there is an interesting relationship between ozone and solar radiation in figure 1 below, plotted using ggplot2.

```{r}
#| label: figure-1
#| echo: true
#| fig-height: 2
#| fig-width: 2
library(ggplot2)
ggplot(airquality,
       aes(x = Ozone,
           y = Solar.R)) + 
  geom_point()

```

We can also see that there is an interesting relationship between Ozone and temperature.

```{r}
#| label: figure-2
#| echo: false
#| fig-height: 2
#| fig-width: 2

ggplot(airquality,
       aes(x = Ozone,
           y = Temp)) + 
  geom_point()

```

We use the knitr package to make a table - CITATION NEEDED!

```{r}
#| label: print-coef-table

knitr::kable(coef(lm_fit))

```

# References
