---
title: "Exploring gapminder"
author: "Your Name"
format: 
  html:
    fig-align: "center"
    fig-width: 4
    fig-height: 4
    fig-format: png
execute: 
  echo: true
  cache: false
---

```{r}
#| label: library
#| echo: false
#| message: false
library(tidyverse)
library(broom)
library(knitr)
```

```{r}
#| label: functions
#| echo: false
# A function to scale input to 0-1
scale_01 <- function(x){
  (x - min(x, na.rm = TRUE)) / diff(range(x, na.rm = TRUE))
}
```

```{r}
#| label: data-read-in
gapminder <- read_csv(here::here("data","gapminder.csv"))
```

Here are the first 6 rows of data

```{r}
#| label: gapminder-top
 top_gap <- head(gapminder, n = 10)
 bot_gap <- tail(gapminder, n = 10)
 
 knitr::kable(top_gap,
              caption = "The first 6 rows of the dataset, gapminder",
              digits = 2)
 kable(bot_gap)
```


```{r}
#| label: demo
#| eval: true
#| echo: true
1 + 1
```

# Introduction

let's look at the lifespan

```{r}
#| label: hist-life-exp
hist(gapminder$lifeExp)
```

Let's look at the GDP per capita

```{r}
#| label: example-cache
hist(gapminder$gdpPercap)
```

Let's fit a simple linear model of the effect of year on life expectancy

```{r}
#| label: example-lm
fit <- lm(lifeExp ~ year, data = gapminder)
fit
```

And let's look at the coefficient table:

```{r}
#| label: coef-table
fit_coef <- tidy(fit)
knitr::kable(fit_coef,
             caption = "A table of the coefficients")
year_slope <- round(fit_coef$estimate[2], 3)
```

The effect of year on life expectancy is `r year_slope`.

# A table of the coefficients is:

```{r}
#| label: table-coef
knitr::kable(fit_coef)
```

```{r}
1+1 

x <- 1 + 1 + 6
```

```{r}
#| label: gg-oz-plot
#| fig-cap: Life expectancy from 1952 - 2007 for Australia. Life expentancy increases
#|   steadily except from 1962 to 1969. We can safely say that our life expectancy is
#|   higher than it has ever been!
library(ggplot2)
library(dplyr)
gapminder %>%
  filter(country == "Australia") %>%
  ggplot(aes(x = year,
             y = lifeExp)) + 
  geom_point()
```

Australia's life expectancy has increased a great deal over the past 50 years

(See Figure \@ref(fig:gg-oz-plot))


# References

